---
title: "Neural Network tests with neuralnet package"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
ptStart <- proc.time()
library(ISLR)
library(e1071)
library(neuralnet)
library(ggplot2)
library(scatterplot3d)
library(class)
library(GGally)
knitr::opts_chunk$set(echo = TRUE)
```


## Model banknote authentication data

```{r banknotedatann}
# Get information from dataset
banknote <- read.table("data\\data_banknote_authentication.txt", sep = ",")
# Naming the columns
colnames(banknote) <- c("variance","skewness" , "curtosis", "entropy", "classoutcome")

# Define dataframe to store the errors
dferror <- NULL

# Define the number of simulations
ntries <- 1:30

# Loop to run simulations
for (itry in ntries) {
  
  # Resample validation training and test dataset - Bootstrap
  idxboot <- sample(nrow(banknote), nrow(banknote), replace = TRUE)
  btrain  <- banknote[unique(idxboot),]
  btrain.svm <- btrain
  btrain.svm$classoutcome <- as.factor(btrain.svm$classoutcome)
  btest   <- banknote[-idxboot,]
  
  ############# NN Model ##############
  
  # Loop to run 1..6 nodes
  for (inodes in 1:6) {
    
    #print(paste("Try :",itry, " Nodes :", inodes))
    
    # Fit Neural Network model.
    nn.model <- neuralnet(classoutcome ~ variance + skewness, data = btrain[,1:5], hidden = inodes, linear.output = FALSE, threshold = 0.04)
  
    # Predict and compute the error test. 
    nn.predi <- compute(nn.model, btest[,1:2])
    nn.resul <- ifelse(nn.predi$net.result >= 0.5, 1, 0)
    nn.tbl   <- table(predict=nn.resul, true=btest[,5] )
    nn.err   <- 1-(sum(diag(nn.tbl)/sum(nn.tbl)))
  
    # Store the error test
    dferror <- rbind(dferror, data.frame(try=itry, method=paste0("NN-",inodes), error=nn.err))
  }
  
  ############# KNN Model ##############
  
  # Loop to run 5..10 Ks
  for (ik in 5:10)  {
    
    #print(paste("Try :",itry, " K :", ik))
    
    # Fit the model and predict
    pred.out  <- knn(btrain[,1:2], btest[,1:2], btrain[,5], k = ik)
    
    # Calculate error.
    tblerr <- table(predict=pred.out, truth=btest[,5])
    err.true <- 1-(sum(diag(tblerr))/sum(tblerr))

    # Store the error
    dferror <- rbind(dferror, data.frame(try=itry, method=paste0("KNN-",ik), error=err.true))
      
  }
  
  
  ############# SVM Model ##############
  #print(paste("Try :",itry, " SVM"))
  
  # Fit the model
  svm.fit <- svm(classoutcome ~ variance + skewness, btrain.svm, kernel = "radial", cost=1, gamma=1)
  
  # Preidct and compute the test error.
  pred.out <- predict(svm.fit, btest[,1:2])
  tblerr <- table(predict=pred.out, truth=btest[,5])
  err.true <- 1-(sum(diag(tblerr))/sum(tblerr))

  # Store the error 
  dferror <- rbind(dferror, data.frame(try=itry, method="SVM", error=err.true))

}

  
ggplot(dferror, aes(x=as.factor(method), y=error, color = as.factor(method))) + geom_boxplot()

```

**For this sample I used only the two most correlated fields of the dataset (variance and skewness). I also used the best knn and svm models.**

**With the exception of the neural network with only 1 node, the other methods had a very similar performance.**
**The neural network may perform similarly to other methods, depending on the type of dataset and the number of observations.**

# Session info {-}

```{r}
sessionInfo()
```

The time it took to knit this file from beginning to end is about (seconds):

```{r}
proc.time() - ptStart
```
